Modular Model-Checking for Fault-Tolerant Distributed System Implementations

### 2016-11-30 doc/om-paper/paper.tex
pervasive paper edits.

\begin{abstract}
With proof techniques like IC3 and $k$-induction with user-supplied
invariants, model-checking scales further than ever before.  Still,
fault-tolerant distributed systems are particularly challenging to
model-check given their large state space and non-determinism. The
typical approach to controlling complexity is to construct ad-hoc
abstractions of faults, message-passing, and behaviors.  However,
these abstractions come at the price of divorcing the model from its
implementation and make refactoring difficult. In this work, we
present a systematic model for fault-tolerant distributed system
verification that combines calendar automata, synchronous observers,
and abstract state machines specialized for model-checking. We
demonstrate the efficacy of the framework by presenting the first
model-checked \emph{implementation} of the Hybrid Oral Messages
algorithm, using a fast majority vote, then demonstrate how
modifications along axes such as the fault model, topology, and node
behavior require only local modifications to the model and proofs.
\end{abstract}

@@

There are at least two classes of abstractions that separate traditional models of fault-tolerant distributed algorithms from their implementations. One is to intertwine the environmental model with the system description. For example, the behavior of nodes is naturally specified as a transition system in which transitions are guarded by the node's fault state. But faults are part of the environment; in an implementation, does not change behavior based on its faults. Another class of abstractions is used to simplify models. For example, message passing might be abstracted with shared state, or a node's local behavior---e.g., a majority vote---is elided and instead, the output is constrained by a \emph{specification} of a majority vote.

In this paper, we develop a formal model to address these concerns. We combine ideas from the literature and folklore to build scalable and modular formal models of fault-tolerant distributed systems. We describe a generic formal model for fault-tolerant distributed systems that aims to reduce the need for ad-hoc verification abstractions and optimizations while maintaining scalability in Section~\ref{sec:model}. There are three aspects of the model: (1) \emph{calendar automata}, originally developed by Dutertre and Sorea~\cite{cal} for specifying real-time systems; (2) \emph{synchronous observers}, originally from the synchronous languages community~\cite{} and popularized by Rushby for model-checking; and (3) \emph{abstract state machines}, useful for abstracting counterexamples. The model is suitable for infinite-state model-checking. With proof techniques like IC3 and $k$-induction, model-checking scales further than ever before~\cite{pdr-kind}.

To demonstrate the model in Section~\ref{sec:byz}, we present a formally-verified implementation of the Oral Messages Hybrid algorithm (OMH)~\cite{}, implementing the Boyer-Moore Fast Majority Vote algorithm for algorithm~\cite{}. The verification is interesting in its own right, as it is the first fully parametric (on the number of nodes) model-checked \emph{implementation} of the algorithm. In Section~\ref{sec:experimental}, we give performance metrics for the model, and we modify the implementation by changing the fault model, topology, node behavior, and show that only local modifications are required to the model and proofs.

@@

\lee{finish intro...  One more contribution is that we abstract faults using partially interpreted functions in model-checking, which is new? Note focus is on infinite-state model-checking: will need user-provided lemmas. compositional approach to providing lemmas. note verification interesting in its own right. verification goes beyond what has been done in thm provers }

@@

\subsection{Calendar Automata}\label{sec:calendar}
\emph{Timed automata} are specialized formalisms for verifying real-time systems~\cite{}. Timed automata assume the existence of continuously-varying real-valued variables, known as \emph{real-time clocks} in a solver. Timed automata model-checkers are specialized for verifying real-time systems in which the only infinite-valued variables are the real-time clocks. Modern general-purpose model-checkers like \lee{name some} use SMT solvers for general infinite-state system verification that is not limited to real-time clocks.

@@

\subsection{Synchronous Observers}\label{sec:sync}
Synchronous observers are state machines that are synchronously composed with a system specification to check properties over the system's state variables. Synchronous observers are a method for composing specifications with a program. Synchronous observers were first introduced in the context of the synchronous programming languages, such as Lustre~\cite{}. While synchronous observers have been part of model-checking folklore for some time, Rushby systematically describes their application to the domain~\cite{}. The general form for specifying a system using synchronous observers is the following:
$$\mathcal{S} | \mathcal{E} | \mathcal{A} | \mathcal{R}$$
\noindent
where `$|$' denotes synchronous composition of transition systems (defined formally below). $\mathcal{S}$ is the \emph{system}, or machine to be realized in an implementation. $\mathcal{E}$ is the \emph{environment} in which the system operates. For example, the environment can be used to specify the behavior of faults in the system. $\mathcal{A}$ are the \emph{assumptions} on the system, and $\mathcal{R}$ are the \emph{requirements}. Synchronous observers can be thought of as a generalization of state predicates,like Hoare triples~\cite{}, to transitions systems.

We define synchronous composition more precisely below, beginning with some preliminary definitions:

@@

\begin{definition}[Deadlock]
$M$ is deadlocked iff either the set of initial states $I$ is empty, or there exists a state $s_0 \in S$ and state $s_1 \in I$ such that $s_0$ is reachable from $s_1$ and there exists no $s_2 \in S$ such that $s_0 \rightarrow s_2$.
\end{definition}

@@

\begin{definition}[Transition system refinement]
$M \subseteq M'$ if and only if $S \subseteq S'$, $I \subseteq I'$, and $\rightarrow \subseteq \rightarrow'$.
\end{definition}

By convention, the assumptions $\mathcal{A}$ should be a refinement of the system $\mathcal{S}$ and environment $\mathcal{E}$. The system is \emph{realizable}~\cite{} under its assumptions if $\mathcal{S} | \mathcal{E} | \mathcal{A}$ is not deadlocked. A system is \emph{correct} if $\mathcal{S} | \mathcal{E} | \mathcal{A}$ refines the requirements $\mathcal{R}$.

There are two practical benefits of the synchronous observer approach. First, the system $\mathcal{S}$ contains no extraneous modeling context about the environment, assumptions, or requirements, making it easier to decompose $\mathcal{S}$ and to synthesize an implementation directly from it. Second, as described by Rushby~\cite{}, requirements can be specified using transition systems rather than temporal logic formula, which is often more natural.

\subsection{The Synchronous Kibitzer}\label{sec:kibitzer}
\lee{We use synchronous composition to implement fault injection. Mention in the intro. This is fundamental to the model, so we have section devoted to it.}
In Section~\ref{sec:sync}, we mentioned an environment transition system synchronously composed with the requirements, system, and assumptions. A particularly important part of the environment is the model of faults, which we address here. The typical approach to injecting faults into a formal model of a distributed system is to add new state variables (or increase the domain of existing state variables) to each process representing its fault state. Then additional state variables are added to represent the nondeterminism introduced by faults into the state or messages by a process.

@@

Not only is modeling faults expensive, but it is generally non-compositional insofar as the fault model pervades the entire model; for example, consider the model of Oral Messages presented by Rushby~\cite{}.

@@

To address these problems, we introduce a synchronous observer that injects faults that we call a \emph{synchronous kibitzer}. The kibitzer decomposes the state and transitions associated with the fault model from the system. For the sake of concreteness, we introduce a particular fault model, the hybrid fault model of Thambidurai and Park~\cite{}. The fault model distinguishes Byzantine (or arbitrary), symmetric, and manifest faults. This fault model applies to broadcast systems, in which a process is expected to broad the same value to multiple receivers. A \emph{Byzantine fault} is one in which a process that is intended to broadcast the same value to other processes may instead broadcast arbitrary values to different receivers (including no value or the correct value). A \emph{symmetric fault} is one in which a process may broadcast the same, but incorrect, value to other processes, and a \emph{manifest fault} is one in which a process's broadcast fault is detectable by the receivers; e.g., by performing a cyclic redundancy check (CRC) or because the value arrives outside of a predetermined window.

In specifying a fault-tolerant system, we must also specify a \emph{maximum fault assumption} (MFA), which specifies the maximum number of of each kind of fault that may be present in the system for some system property to hold. Define a enumeration of fault types $$\textnormal{FAULT\_TYPE} = \{none, byz, sym, man\}$$ As in the previous section, let $Id \subset \mathbb{N}$ be a finite set of indices, and let the variable $$faults: Id \rightarrow \textnormal{FAULT\_TYPE}$$ range over possible mappings from process indices to faults.

@@

\lee{Talk about how to define an MFA in the environment}

% ------------------------------------------------------------
\subsection{Abstract State Machines}\label{sec:abstract}\label{sec:asms}
In model-checking, counterexamples to properties are traces of states. A state is a collection of variable values, and in large models, there are a lot. A single state includes assignments to each of the variables, and counterexample trace may be many 10s of states in length. In practice, counterexamples depend on a small number of state variables. The user has to manually separate the state variables that matter from those that do not for a specific property. It is not enough prevent variables that stutter from displaying since some state variables might be updated without affecting the property. The problem is particularly pertinent when model-checking models that have sufficient detail for implementation synthesis, as is the goal in our work.

Systems are usually designed in modes such that predicates on state variables are parameterized on which mode the system is in. The transition between modes implements a finite state-machine. The modes and the state-machine are usually implicit, but a property violation usually requires an unexpected mode transition. Abstracting counterexample traces over all of the state variables by traces over the modes helps to identify why a property fails quickly.

Our solution to the problem of constructing a mode-based state machine uses abstract state machines (ASMs). ASMs are a generalization of finite state machines originally developed by Gurevich to generalize state machines to operate over arbitrary data structures~\cite{asm}.

In our context, we require only a restricted form of ASMs known as a \emph{sequential small-step ASM}:

@@

\lee{note that the ASM is not a refinement.}

@@

To demonstrate the model and techniques, we model the Oral Messages Hybrid (OMH) algorithm~\cite{}, a more sophisticated version of the class Oral Messages (OM) algorithm. OM was first formulated by Lamport, Shostak, and Pease~\cite{om} to achieve agreement in a distributed system while tolerating Byzantine faults. OMH was originally developed by Thambidurai and Park~\cite{hybrid} to achieve the same result in the presence of a more sophisticated fault model that includes symmetric and benign faults. However, OMH had a bug, as originally formulated, which was corrected and formally verified by Lincoln and Rushby~\cite{csl-93-2}.

@@

To make the proof scalable, we specify inductive invariants to be used by SAL's $k$-induction engine. The invariants are modular. There are 11 invariants, falling into five categories:
\begin{enumerate}
  \item \emph{Calendar automata}: Lemmas relating to the calendar automata model. These include lemmas such as time being monotonic, channels missing messages if there is no calendar event, and only nodes associated with a calendar event may execute their local state machines.
  \item \emph{Abstract state machine (ASM)}: Lemmas relating the ASM synchronous observer states to the implementation states.
  \item \emph{Lieutenant local state-machine (SM) behavior}: Lemmas describing the modes of behavior of the lieutenants. The major modes of the state machine are receiving messages, then once it has filled its buffer, it votes, and after voting returns the result. One additional lemma notes that the messages currently received plus missing messages equals the total number of expected messages.
  \item \emph{Faults}: Lemmas characterizing the effect of a fault in a single broadcast. Examples include lemmas stating that if a node receives a faulty message, some ``upstream'' node in the communication path was faulty. Another example is that the faults of messages latched by a node in its buffer match the faults ascribed to the sender in the calendar event.
  \item \emph{Voting}: Lemmas proving that the Fast Majority Vote algorithm implements a majority vote, if one exists. These lemmas are nearly verbatim transcriptions from the journal proofs~\cite{mjrty}.
\end{enumerate}
\noindent
The proof structure is shown in Figure~\ref{fig:proof}. The number of lemmas per category are shown in parentheses. Arrows denote dependencies. For example, the ASM lemmas depend on both the calendar automata and lieutenant state-machine lemmas. As can be seen, the proof structure is quite modular. The calendar lemmas are general and independent of any particular protocol or fault model. Similarly, lemmas about the internal behavior of a lieutenant is independent of the global protocol behavior. It is also independent of the effect of faults on the system---the only ``knowledge'' of faults that lieutenant has is whether a fault is benign or not. Lemmas about the behavior of faults in the system are also independent of the particular protocol being modeled. Likewise, lemmas about the particular voting algorithm used depend only on the lieutenant's internal behavior. Only the ASM depends on both calendar-specific and local state-machine results, since it is an abstraction of the entire system implementation. Recall, however, that the ASM is a convenience for debugging and can be elided.

@@

@@

Using automated techniques, Gasc{\'{o}}n and Tiwari use SAT-based bounded synthesis to partially synthesize a variant of Oral Messages that tolerates transient faults~\cite{om1-synth}. Bokor~\emph{et~al.} describe a message-passing model for synchronous distributed algorithms that is particularly amenable to partial-order reduction for explicit-state model-checking~\cite{Bokor2010}. That said, their model of OM(1) (not OMH(1)), timeouts after 10~hours, and we assume a voting algorithm is not explicitly specified. Very recently, Jovanovi{\'{c}} and Dutertre use a ``flattened'' high-level model of OM(1) as a benchmark for IC3 augmented with $k$-induction~\cite{pdr-kind}.

>>>>

\begin{abstract}
With proof techniques like IC3 and $k$-induction, model-checking scales further
than ever before.  Still, fault-tolerant distributed systems are particularly
challenging to model-check given their large state space and
non-determinism. The typical approach to controlling complexity is to construct
ad-hoc abstractions of faults, message-passing, and behaviors.  However, these
abstractions come at the price of divorcing the model from its implementation
and make refactoring difficult. In this work, we present a systematic model for
fault-tolerant distributed system verification that combines calendar automata,
synchronous observers, and abstract state machines specialized for
model-checking. We demonstrate the efficacy of the framework by presenting the
first model-checked \emph{implementation} of the Hybrid Oral Messages algorithm,
using a fast majority vote, then demonstrate how modifications along axes such
as the fault model, timing constraints, and local node behavior require only local modifications
to the model and proofs. This work is carried out in SAL.
\end{abstract}

@@

There are at least two classes of abstractions that separate traditional models of fault-tolerant distributed algorithms from their implementations. One is to intertwine the environmental model with the system description. For example, the behavior of nodes is naturally specified as a transition system in which transitions are guarded by the node's fault state. But faults are part of the environment; an implementation does not use its own fault status to choose actions! Another class of abstractions is used to simplify models. For example, message passing might be abstracted with shared state, or a node's local behavior is elided and instead, the output is constrained by a \emph{specification} of the behavior.

In this paper, we develop a formal model to address these concerns. We combine ideas from the literature and folklore to build scalable and modular formal models of fault-tolerant distributed systems. We describe a generic formal model for fault-tolerant distributed systems that aims to reduce the need for ad-hoc verification abstractions and optimizations while maintaining scalability in Section~\ref{sec:model}. There are three aspects of the model: (1) \emph{calendar automata}, originally developed by Dutertre and Sorea~\cite{cal} for specifying real-time systems; (2) \emph{synchronous observers}, originally from the synchronous languages community~\cite{} and popularized by Rushby for model-checking~\cite{}; and (3) \emph{abstract state machines}, useful for abstracting counterexamples. The model is suitable for infinite-state model-checking.

To demonstrate the model in Section~\ref{sec:byz}, we present a formally-verified implementation of the Oral Messages Hybrid algorithm (OMH)~\cite{}, implementing the Boyer-Moore Fast Majority Vote algorithm for algorithm~\cite{}. The verification is interesting in its own right, as it is the first fully parametric (on the number of nodes) model-checked \emph{implementation} of the algorithm. In Section~\ref{sec:experimental}, we give performance metrics for the model. First, we benchmark the model, showing that despite the additional complexity, it scales farther than other model-checking verifications at the algorithmic level. The scalability is due principally to specifying invariants and using $k$-induction in SRI's SAL model-checker~\cite{}. Developing invariants requires some user guidance. A user should not have to discover all new invariants for new protocols or implementations. We show that most of the lemmas required are not protocol specific and are modular, concerning only specific aspects of the system. To demonstrate this, we modify the OHM implementation in various ways to show that only local modifications are required to the model and proofs.

Finally, in Section~\ref{sec:related} we describe related work, and we make concluding remarks in Section~\ref{sec:conclusions}.

@@

@@

\subsection{Calendar Automata}\label{sec:calendar}
\emph{Timed automata} are specialized formalisms for verifying real-time systems~\cite{}. Timed automata assume the existence of continuously-varying real-valued variables, known as \emph{real-time clocks} in a solver. Model-checkers for timed-automata are specialized for verifying real-time systems in which the only infinite-valued variables are the real-time clocks.

@@

\subsection{Synchronous Observers}\label{sec:sync}
Synchronous observers are state machines that are synchronously composed with a system specification to check properties over the system's state variables. Synchronous observers are a method for composing specifications with a program. Synchronous observers were first introduced in the context of the synchronous programming languages, such as Lustre~\cite{}. While synchronous observers have been part of model-checking folklore for some time, Rushby systematically describes their application to the domain~\cite{}. In Section~\ref{sec:sync-model} we define synchronous observers and then describe their application to modeling faults in Section~\ref{sec:kibitzer}.

\subsubsection{Model}
A synchronous observer is of the form
$$\mathcal{S} | \mathcal{O}$$
\noindent
where `$|$' denotes synchronous composition of transition systems (defined formally below). $\mathcal{S}$ is the \emph{system}, and $\mathcal{O}$ is the \emph{observer}. We define synchronous composition more precisely below, beginning with some preliminary definitions:

@@

@@

%% \begin{definition}[Transition system refinement]
%% $M \subseteq M'$ if and only if $S \subseteq S'$, $I \subseteq I'$, and $\rightarrow \subseteq \rightarrow'$.
%% \end{definition}

%% By convention, the assumptions $\mathcal{A}$ should be a refinement of the system $\mathcal{S}$ and environment $\mathcal{E}$. The system is \emph{realizable}~\cite{} under its assumptions if $\mathcal{S} | \mathcal{E} | \mathcal{A}$ is not deadlocked. A system is \emph{correct} if $\mathcal{S} | \mathcal{E} | \mathcal{A}$ refines the requirements $\mathcal{R}$.

%% \begin{definition}[Deadlock]
%% $M$ is deadlocked iff either the set of initial states $I$ is empty, or there exists a state $s_0 \in S$ and state $s_1 \in I$ such that $s_0$ is reachable from $s_1$ and there exists no $s_2 \in S$ such that $s_0 \rightarrow s_2$.
%% \end{definition}

There are two practical benefits of the synchronous observer approach. First, the system $\mathcal{S}$ contains no extraneous modeling context about the environment, assumptions, or requirements, making it easier to decompose $\mathcal{S}$ and to synthesize an implementation directly from it. Second, as described by Rushby~\cite{}, requirements can be specified using transition systems rather than temporal logic formula, which is often more natural. We use synchronous observers for both purposes.

\subsubsection{The Synchronous Kibitzer}\label{sec:kibitzer}
Synchronous observers can be used to model the environment, and in particular, to compositionally inject faults. The typical approach to injecting faults into a formal model of a distributed system is to add new state variables to each process representing its fault state. Then additional state variables are added to represent the nondeterminism introduced by faults into the state or messages by a process.

@@

Not only is modeling faults expensive, but it is generally non-compositional insofar as the fault model pervades the entire model.

@@

To address these issues, we introduce a synchronous observer that injects faults that we call a \emph{synchronous kibitzer}. The kibitzer decomposes the state and transitions associated with the fault model from the system. For the sake of concreteness, we introduce a particular fault model, the hybrid fault model of Thambidurai and Park~\cite{}. The fault model distinguishes Byzantine (or arbitrary), symmetric, and manifest faults. This fault model applies to broadcast systems, in which a process is expected to broad the same value to multiple receivers. A \emph{Byzantine fault} is one in which a process that is intended to broadcast the same value to other processes may instead broadcast arbitrary values to different receivers (including no value or the correct value). A \emph{symmetric fault} is one in which a process may broadcast the same, but incorrect, value to other processes, and a \emph{manifest fault} is one in which a process's broadcast fault is detectable by the receivers; e.g., by performing a cyclic redundancy check (CRC) or because the value arrives outside of a predetermined window.

%% In specifying a fault-tolerant system, we must also specify a \emph{maximum fault assumption} (MFA), which specifies the maximum number of of each kind of fault that may be present in the system for some system property to hold.

Define an enumeration of fault types $$\textnormal{FAULT\_TYPE} = \{none, byz, sym, man\}$$ As in the previous section, let $Id \subset \mathbb{N}$ be a finite set of indices, and let the variable $$faults: Id \rightarrow \textnormal{FAULT\_TYPE}$$ range over possible mappings from process indices to faults.

@@

The upshot is that the fault model and fault-injection is completely modular to the specification of the protocol and node behavior.

% ------------------------------------------------------------
\subsection{Abstract State Machines}\label{sec:abstract}\label{sec:asms}
In model-checking, counterexamples to properties are traces of states. A state is a collection of variable values, and in large models, there are a lot. A single state includes assignments to each of the variables, and the counterexample traces we dealt with (see Section~\ref{sec:experimental}) can contain hundreds of state variables. In practice, counterexamples depend on a small subset of these. The user has to manually separate the state variables that matter from those that do not for a specific property. It is not enough prevent variables that stutter from displaying since some state variables might be updated without affecting the property. The problem is particularly pertinent when model-checking models that have sufficient detail for implementation synthesis, as is the goal in our work.

%% Systems are usually designed in modes such that predicates on state variables are parameterized on which mode the system is in. The transition between modes implements a finite state-machine. The modes and the state-machine are usually implicit, but a property violation usually requires an unexpected mode transition. Abstracting counterexample traces over all of the state variables by traces over the modes helps to identify why a property fails quickly.

But the relationship between many of the state variables have an intuitive structure that can be characterized by a state machine imposed over it. The state machine describes discrete modes or configurations. Each mode captures a relation on a subset of the state variables, as well as the set of possible modes that follow.

The idea is an implementation of abstract state machines (ASMs). ASMs are a generalization of finite state machines originally developed by Gurevich to generalize state machines to operate over arbitrary data structures~\cite{asm}. In our context, we require only a restricted form of ASMs known as a \emph{sequential small-step ASM}:

@@

\lee{probably need an example here.}

@@

To demonstrate the model and techniques, we model an implementation of the Oral Messages Hybrid (OMH) algorithm~\cite{}, a more sophisticated version of the class Oral Messages (OM) algorithm. OM was first formulated by Lamport, Shostak, and Pease~\cite{om} to achieve agreement in a distributed system while tolerating Byzantine faults. OMH was originally developed by Thambidurai and Park~\cite{hybrid} to achieve the same result in the presence of a more sophisticated fault model that includes symmetric and benign faults. However, OMH had a bug, as originally formulated, which was corrected and formally verified by Lincoln and Rushby using interactive theorem-proving~\cite{csl-93-2}.

@@

To make the proof scalable, we specify inductive invariants to be used by SAL's $k$-induction engine. There are 11 invariants, falling into five categories:
\begin{enumerate}
  \item \emph{Calendar automata}: Lemmas relating to the calendar automata model. These include lemmas such as time being monotonic, channels missing messages if there is no calendar event, and only nodes associated with a calendar event may execute their local state machines.
  \item \emph{Abstract state machine (ASM)}: Lemmas relating the ASM synchronous observer states to the implementation states.
  \item \emph{Lieutenant local state-machine (SM) behavior}: Lemmas describing the modes of behavior of the lieutenants. The major modes of the state machine are receiving messages, then once it has filled its buffer, it votes, and after voting returns the result. One additional lemma notes that the messages currently received plus missing messages equals the total number of expected messages.
  \item \emph{Faults}: Lemmas characterizing the effect of a fault in a single broadcast. Examples include lemmas stating that if a node receives a faulty message, some ``upstream'' node in the communication path was faulty. Another example is that the faults of messages latched by a node in its buffer match the faults ascribed to the sender in the calendar event.
  \item \emph{Voting}: Lemmas proving that the Fast Majority Vote algorithm implements a majority vote, if one exists. These lemmas are nearly verbatim transcriptions from the journal proofs~\cite{mjrty}.
\end{enumerate}
\noindent
The proof structure is shown in Figure~\ref{fig:proof}. The number of lemmas per category are shown in parentheses. Arrows denote dependencies. For example, the ASM lemmas depend on both the calendar automata and lieutenant state-machine lemmas. As can be seen, the proof structure is quite modular. The calendar lemmas are general and independent of any particular protocol or fault model. Similarly, lemmas about the internal behavior of a lieutenant is independent of the global protocol behavior. It is also independent of the effect of faults on the system---the only ``knowledge'' of faults that lieutenant has is whether a fault is benign or not. Lemmas about the behavior of faults in the system are also independent of the particular protocol being modeled. Likewise, lemmas about the particular voting algorithm used depend only on the lieutenant's internal behavior. Only the ASM depends on both calendar-specific and local state-machine results, since it is an abstraction of the entire system implementation. Recall, however, that the ASM is a convenience for debugging and can be elided.

@@

\lee{discuss results}

@@

Using automated techniques, Gasc{\'{o}}n and Tiwari use SAT-based bounded synthesis to partially synthesize a variant of Oral Messages that tolerates transient faults~\cite{om1-synth}. Bokor~\emph{et~al.} describe a message-passing model for synchronous distributed algorithms that is particularly amenable to partial-order reduction for explicit-state model-checking~\cite{Bokor2010}. That said, their model of OM(1) (not OMH(1)), timeouts after 10~hours, and we assume a voting algorithm is not explicitly specified. \lee{for what size? Also, Rushby's model?} Very recently, Jovanovi{\'{c}} and Dutertre use a ``flattened'' high-level model of OM(1) as a benchmark for IC3 augmented with $k$-induction~\cite{pdr-kind}.
